### 2015-01-16 src/conclusion.Rnw
update

Our analysis suggests that while some of the different strategies produce
slightly advantageous mutation subsets, overall, the advantage thus gained
is very little. None of the common operator selection strategies performed
consistently well against random sampling while using either the utility or
the mutation effectiveness criteria. While some of the individual operators
such as \Pitrv, \Piti, \Pitri, and \Pites show promise in test utility,
they do not stand out when we examine the mutation effectiveness in comparison
to baseline.

>>>>

Our analysis suggests that while some of the different strategies produce
slightly advantageous mutation subsets, overall, the advantage thus gained
is very little. None of the common operator selection strategies performed
consistently well against random sampling while using either the utility or
the mutation effectiveness criteria. While some of the individual operators
such as \Pitrv, \Piti, \Pitri, and \Pites~show promise in test utility,
they do not stand out when we examine the mutation effectiveness in comparison
to baseline.
